A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-20 tex/body.tex
due to the fact that -> because (or since)
fit again

%The last precondition is admittedly rather technical.
Ensuring disequality constraints are satisfied by an interpretation based on $\ValC$
relies on showing that $\ValC$ is injective modulo $\alpha$-equivalence.
The last precondition in the above rule ensures that $\ValC$ remains injective after each substitution.
More precisely, the set $\Terms_{\smash{\J}}^{\Varec{x}}(\ValC)$ is an overapproximation of the values
that, when assigned to ${\Varec{x}}$, cause values in the range of $\ValC$ to become $\alpha$-equivalent.
This precondition is not strictly necessary in practice, 
as one could compute $\nf{\ValC [ {\Varec{x}} \mapsto \MU {\Varec{x}}.\; t ]}$ optimistically and check
injectivity afterward, repeating until a suitable value is found.
For infinite codatatypes, it is always possible to find suitable values $v$,
due to the fact that $\Terms_{\smash{\J}}^{\Varec{x}}(\ValC)$ is a finite set.
%Injectivity is important to satisfy disequality constraints.
%For infinite codatatypes, it is always possible to find suitable values $v$.
%For example,
%if the longest cycle in $\Terms_{\smash{\J}}^{\Varec{x}}(\ValC)$ is of length $n$, a fresh value
%can be constructed with a cycle of length $n + 1$.

>>>>

%The last precondition is admittedly rather technical.
Ensuring disequality constraints are satisfied by an interpretation based on $\ValC$
relies on showing that $\ValC$ is injective modulo $\alpha$-equivalence.
The last precondition in the above rule ensures that $\ValC$ remains injective after each substitution.
More precisely, the set $\Terms_{\smash{\J}}^{\Varec{x}}(\ValC)$ is an overapproximation of the values
that, when assigned to ${\Varec{x}}$, cause values in the range of $\ValC$ to become $\alpha$-equivalent.
%This precondition is not strictly necessary in practice, 
%as one could compute $\nf{\ValC [ {\Varec{x}} \mapsto \MU {\Varec{x}}.\; t ]}$ optimistically and check
%injectivity afterward, repeating until a suitable value is found.
For infinite codatatypes, it is always possible to find suitable values $v$,
because $\Terms_{\smash{\J}}^{\Varec{x}}(\ValC)$ is a finite set.
%Injectivity is important to satisfy disequality constraints.
%For infinite codatatypes, it is always possible to find suitable values $v$.
%For example,
%if the longest cycle in $\Terms_{\smash{\J}}^{\Varec{x}}(\ValC)$ is of length $n$, a fresh value
%can be constructed with a cycle of length $n + 1$.
